|

### 2020-05-25 paper/Manuscript.Rmd
Update paper and vignette

author:
  - name: "Caspar J. Van Lissa"
    institution: "1,2"
    orcid: "0000-0002-0808-5024"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    institution: "3,4"
    orcid: "0000-0001-8765-6982"
  - name: "Loek Brinkman"
    institution: "2,5"
    orcid: "0000-0003-3997-1173"
  - name: "Aaron Peikert"
    institution: "3,6"
    orcid: "0000-0001-7813-818X"
  - name: "Barbara M.I. Vreede"
    institution: "7"
  - name: "Anna-Lena Lamprecht"
    institution: "2,8"
    orcid: "0000-0002-5023-4601"

affiliation:
  - id: "1"
    institution: "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id: "2"
    institution: "Open Science Community Utrecht"
  - id: "3"
    institution: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id: "4"
    institution: "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK"
  - id: "5"
    institution: "UMC Utrecht"
  - id: "6"
    institution: "Humboldt-Universitaet zu Berlin"
  - id: "7"
    institution: "University Library Utrecht"
  - id: "8"
    institution: "Utrecht University, Department of Information and Computing Sciences"

abstract: |
  Adopting open science
  principles can be challenging and costly, because doing so requires
  substantial conceptual education and training in the use of new tools. The 
  goal of this paper is to remove these obstacles. We introduce the Workflow for
  Open Reproducible Code in Science (WORCS). WORCS constitutes a step-by-step
  procedure that researchers can follow to make an entire project open and
  reproducible. It is based on best practices, and can be used either in
  parallel to, or in absence of, top-down requirements by journals,
  institutions, and funding bodies. To facilitate widespread adoption, the
  WORCS principles are implemented in the R-package `worcs`, which offers an
  RStudio 
  project template that is, effectively, a "one-click solution" for R users. 
  This paper introduces the workflow, discusses how it meets different 
  requirements of open science, and provides examples of the implementation of
  `worcs` in R.

@@

Alternatively, if the project requires data to remain closed, researchers can
call `closed_data(data)`. This function also stores the data in a local `.csv` file
and generates a codebook,
but the original data file is added to `.gitignore` so it cannot be
accidentally added to the 'Git' repository.
The function also computes a checksum for the original data, and logs it in the
`.worcs` project file. This checksum serves as the indelible record of the state 
of the raw data.
The function `closed_data()` also creates a synthetic dataset (called
`synthetic_data.csv` by default).
The user should push all changed files to the remote repository.
Once the remote repository is made public, people will have access to a
checksum for the original data that exist on your local machine, a codebook
describing those data, and a synthetic copy of the data.

<!-- Maybe remark that in the "closed" case, a the data should be backupped somewhere else, as GitHub will not do the job in this setting. -->

@@

Being familiar
with 'Git' remote repositories like GitHub opens doors to new forms of collaboration:
In the open source
software community, continuous peer review and voluntary collaborative acts by
strangers who are interested in a project are commonplace
[see @adolphOpenBehavioralScience2012].  This kind of collaboration is budding
in scientific software development as well; for example, the lead author of this
paper became a co-author on several R-packages after submitting pull requests
with bug fixes or additional functionality [@rosenbergTidyLPAPackageEasily2018; @hallquistMplusAutomationPackageFacilitating2018], and two co-authors of this
paper became involved by contributing pull requests to `worcs`. It is also
possible to invite such collaboration by 
[opening Issues](https://help.github.com/en/github/managing-your-work-on-github/about-issues)
for tasks that still need to be accomplished, and tag known Collaborators to
address them, or invite external collaborators to contribute their expertise.

>>>>

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    affiliation: "3,4"
  - name: "Aaron Peikert"
    affiliation: "3,5"
  - name: "Barbara Vreede"
    affiliation: "6"
  - name: "Anna-Lena Lamprecht"
    affiliation: "2,7"
    email: "a.l.lamprecht@uu.nl"
  - name: "Loek Brinkman"
    affiliation: "2,8"
  - name: "Marijn E. Struiksma"
    affiliation: "2,9"

affiliation:
  - id: "1"
    institution: "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id: "2"
    institution: "Open Science Community Utrecht"
  - id: "3"
    institution: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id: "4"
    institution: "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK"
  - id: "5"
    institution: "Humboldt-Universitaet zu Berlin"
  - id: "6"
    institution: "University Library Utrecht"
  - id: "7"
    institution: "Utrecht University, Department of Information and Computing Sciences"
  - id: "8"
    institution: "UMC Utrecht"
  - id: "9"
    institution: "Utrecht Institute of Linguistics OTS"

abstract: |
  Adopting open science
  principles can be challenging and time-intensive, because doing so requires
  substantial conceptual education and training in the use of new tools. The 
  goal of this paper is to remove these obstacles. We introduce the Workflow for
  Open Reproducible Code in Science (WORCS). WORCS constitutes a step-by-step
  procedure that researchers can follow to make an entire project open and
  reproducible. It is based on best practices, and can be used either in
  parallel to, or in absence of, top-down requirements by journals,
  institutions, and funding bodies. To facilitate widespread adoption, the
  WORCS principles are implemented in the R-package `worcs`, which offers an
  RStudio 
  project template that is, effectively, a "one-click solution" for R users. 
  This paper introduces the workflow, discusses how it meets different 
  requirements of open science, and provides examples of the implementation of
  `worcs` in R.

@@

Alternatively, if the project requires data to remain closed, researchers can
call `closed_data(data)`. This function also stores the data in a local `.csv` file
and generates a codebook,
but the original data file is added to `.gitignore` so it cannot be
accidentally added to the 'Git' repository.
The function also computes a checksum for the original data, and logs it in the
`.worcs` project file. This checksum serves as the indelible record of the state 
of the raw data.
The function `closed_data()` also creates a synthetic dataset (called
`synthetic_data.csv` by default).
The user should push all changed files to the remote repository.
Once the remote repository is made public, people will have access to a
checksum for the original data that exist on your local machine, a codebook
describing those data, and a synthetic copy of the data.
Keep in mind that, when using closed data, the original data file exists only on
the user's computer. Adequate provisions to back up the data, while respecting
principles of responsible data stewardship, should be made.

@@

Being familiar
with 'Git' remote repositories opens doors to new forms of collaboration:
In the open source
software community, continuous peer review and voluntary collaborative acts by
strangers who are interested in a project are commonplace
[see @adolphOpenBehavioralScience2012].  This kind of collaboration is budding
in scientific software development as well; for example, the lead author of this
paper became a co-author on several R-packages after submitting pull requests
with bug fixes or additional functionality [@rosenbergTidyLPAPackageEasily2018; @hallquistMplusAutomationPackageFacilitating2018], and two co-authors of this
paper became involved by contributing pull requests to `worcs`. It is also
possible to invite such collaboration by 
[opening Issues](https://help.github.com/en/github/managing-your-work-on-github/about-issues)
for tasks that still need to be accomplished, and tag known Collaborators to
address them, or invite external collaborators to contribute their expertise.
